---
title: "Spatial Analysis"
author: "Anastasia Kunz"
date: "2/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(sf)
library(spatstat)
library(maptools) 
library(sp)
library(raster)
library(tmap)
```

Point pattern analysis with density plot, and the G- and L- function (distance methods) to compare our observed points with simulated complete spatial randomness

```{r}
voles <- read_sf(dsn = here("redtreevoledata"),
                 layer = "ds033") %>%  #you dont have to select the shpfile
  dplyr::select(COUNTY) %>% 
  filter(COUNTY == "HUM") %>% #Humbolt county
  st_transform(crs = 4326)

plot(voles)
```

```{r}
#get humboldt county outline

humboldt <- read_sf(dsn = here("redtreevoledata"),
                    layer = "california_county_shape_file") %>% 
  filter(NAME == "Humboldt") %>% 
  dplyr::select(NAME)

st_crs(humboldt) <- 4326

ggplot()+
  geom_sf(data = humboldt,
          color = "darkorchid",
          fill = "darkorchid4",
          size = 1)+
  geom_sf(data = voles,
          color = "orange",
          alpha = 0.7,
          size = 2)+
  theme_minimal()

```


these need to be combined into a spatial point pattern data (points and window combo) this requires a 2D projection, which is UTM in this case. THis is wy there is a proj4string line here to specify the project. Use the spatstat to create point patterns that play nicely with other functions for data viz and point pattern analysis.

```{r}
voles_sp <- as(voles, "Spatial") #convert object to "spatial"

proj4string(voles_sp) <- "+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0" #add UTM projection
```

```{r}
voles_ppp <- as(voles_sp, "ppp") # convert to spatial point pattern

humboldt_sp <-as(humboldt, "Spatial") #Convert to spatial
proj4string(humboldt_sp) <- "+proj=utm +zone=10 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"



```

```{r}
humboldt_win <- as(humboldt_sp, "owin") #convert to spatial point patttern

# Combine as point pattern object (points and window)
voles_full <- ppp(voles_ppp$x, voles_ppp$y, window = humboldt_win)
```

```{r}
plot(voles_full)
```


## Density

voles hotspots by kernel density then change sigma

```{r}
voles_density <- density(voles_full, sigma = 0.04)
plot(voles_density)
```

compare to spatial randomness:

```{r}
wgs84 = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
vole_raster <- raster(voles_density, crs = wgs84)

tmap_mode("view")

tm_shape(vole_raster)+
  tm_raster(midpoint = NA,
            palette = "Reds",
            legend.show = FALSE)
```


## Nearest Neighbor (G Function)

```{r}
r <- seq(0,0.15, by = 0.005)
gfunction <- envelope(voles_full, fun = Gest, r = r, nsim = 100, nrank = 2)

gfunction
```

```{r}
gfunction_long <- gfunction %>% 
  as.data.frame() %>% 
  pivot_longer(cols = obs:hi, names_to = "model", values_to = "g_val")

ggplot(data = gfunction_long, aes(x = r, y = g_val, group = model))+
  geom_line(aes(color = model))

```

```{r}
r2 <- seq(0,0.5, by = 0.05)

lfunction <- envelope(voles_full, fun = Lest, r = r2, nsim = 10, rank = 2, global = TRUE)
```

```{r}
lfunction_long <- lfunction %>% 
  as.data.frame() %>% 
  pivot_longer(cols = obs:hi, names_to = "model", values_to = "k_val")

ggplot(data = lfunction_long, aes(x = r, y = k_val, group = model))+
  geom_line(aes(color = model))
```







