---
title: "Part1_stringr_funct"
author: "Anastasia Kunz"
date: "2/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Detect String Patterns with `str_detect()`

looks for pattern anywhere within the target

```{r}
vec <-c(" A Unicorn   Fish ", " add   cornmeal", "Frenchfries ", "acorn Squash")

str_detect(vec, pattern = "corn")
```

which of these elements contains lower case "corn"?
looks for an exact match
returns a true-false logical

put within a filter function to include true and exclude false

### using star wars

```{r}
walk_subset <- starwars %>% 
  filter(str_detect(name, pattern = "walk"))

#str_subset() does this too in one function if you want to be more efficient

```


### replace a string pattern with something else

for misspellings etc. 

`str_replace` to replace an existing string pattern with something else

```{r}
vec_bren <- str_replace(vec, pattern = "corn", replacement = "COOL")
  
vec_bren
```

replace the pattern "Sky" with pattern "MOON"

```{r}
sw_moonwalk <- starwars %>% 
  mutate(name = str_replace(name, pattern = "Sky", replacement = "MOON"))
```

## Use `str_trim` to remove excess leading and trailing whitespace

```{r}
str_trim(vec)
str_squish(vec)
```

`str_to_lower()` or str_to_upper()

```{r}
str_to_lower(vec)
#also 
str_to_upper(vec)
# but probably wont use it to often
```

## using these in combo

```{r}
sw_combo <- starwars %>% 
  filter(str_detect(name, pattern = "Darth")) %>% 
  mutate(name = str_replace(name, pattern = "Darth", replacement = "Llama")) %>% 
  mutate(name = str_to_lower(name))
```





